---
title: "Assignment 2"
---

The second assignment involves the Advanced Search feature on <https://m.imdb.com/search,> allowing us to list available movie data on IMDb. The task is to scrape the HTML and extract the results. Assignment II consists of four parts.

## Part I

### Defining URLs:

```{r}
#| code-fold: true
#| code-summary: "Show the code"
#Defining the URL for those with a Release Date between 2010 and 2023
url1 <- "https://m.imdb.com/search/title/?title_type=feature&release_date=2010-01-01,2023-12-31&num_votes=2500,&country_of_origin=TR&count=250"
#Defining the URL for those with a Release Date before 2010
url2 <- "https://m.imdb.com/search/title/?title_type=feature&release_date=,2009-12-31&num_votes=2500,&country_of_origin=TR&count=250"
```

## Part II

### Loading necessary libraries:

```{r}
#| code-fold: true
#| code-summary: "Show the code"
library(tidyverse) # for everything :)
library(rvest) # for HTML scraping
library(stringr) # for string processing
library(knitr)
library(ggplot2)
```

### For Titles:

```{r}
#| code-fold: true
#| code-summary: "Show the code"
title1 <- read_html(url1) %>% 
  html_elements(".ipc-title__text") %>% html_text()
title1 <- tail(head(title1,-1),-1)
title1 <- str_split(title1, " ", n=2)
title1 <- unlist(lapply(title1, function(x) {x[2]}))

title2 <- read_html(url2) %>%
  html_elements(".ipc-title__text") %>% html_text()
title2 <- tail(head(title2,-1),-1)
title2 <- str_split(title2, " ", n=2)
title2 <- unlist(lapply(title2, function(x) {x[2]}))
#Combining Titles
Title <- c(title1, title2)
```

### For Years:

```{r}
#| code-fold: true
#| code-summary: "Show the code"
year1 <- read_html(url1) %>%
  html_elements(".dli-title-metadata-item:nth-child(1)") %>%
  html_text() %>% as.numeric()

year2 <- read_html(url2) %>%
  html_elements(".dli-title-metadata-item:nth-child(1)") %>%
  html_text() %>% as.numeric()
#Combining Years
Year <- c(year1, year2)
```

### For Durations :

```{r}
#| code-fold: true
#| code-summary: "Show the code"

convert_time_updated <- function(time_string) {
  total_hours <- 0
  total_minutes <- 0
  
  if (grepl("h", time_string)) {
    time_parts <- strsplit(time_string, "h|m")[[1]]
    if (length(time_parts) >= 1) {
      total_hours <- as.numeric(time_parts[1])
    }
    if (length(time_parts) >= 2) {
      total_minutes <- as.numeric(time_parts[2])
    }
  } else {
    total_minutes <- as.numeric(gsub("m", "", time_string))
  }
  
  total_duration <- total_hours * 60 + total_minutes
  return(total_duration)
}

duration1 <- read_html(url1) %>%
  html_elements(".dli-title-metadata-item:nth-child(2)") %>%
  html_text()
duration1 <- unlist(lapply(duration1, convert_time_updated))

duration2 <- read_html(url2) %>%
  html_elements(".dli-title-metadata-item:nth-child(2)") %>%
  html_text()
duration2 <- unlist(lapply(duration2, convert_time_updated))

Duration <- c(duration1, duration2)
```

### For Ratings :

```{r}
#| code-fold: true
#| code-summary: "Show the code"
rating1 <- read_html(url1) %>%
  html_elements(".ratingGroup--imdb-rating") %>%
  html_text()
rating1 <- str_extract(rating1, "\\d+\\.\\d+") %>%
  as.numeric()

rating2 <- read_html(url2) %>%
  html_elements(".ratingGroup--imdb-rating") %>%
  html_text()
rating2 <- str_extract(rating2, "\\d+\\.\\d+") %>%
  as.numeric()

Rating <- c(rating1, rating2)
```

### For Votes :

```{r}
#| code-fold: true
#| code-summary: "Show the code"
votes1 <- read_html(url1) %>%
  html_elements(".kRnqtn") %>%
  html_text()
votes1 <- gsub("\\D", "", votes1) %>%
  as.numeric()

votes2 <- read_html(url2) %>%
  html_elements(".kRnqtn") %>%
  html_text()
votes2 <- gsub("\\D", "", votes2) %>%
  as.numeric()

Votes <- c(votes1, votes2)
```

### Data Frame :

```{r}
#| code-fold: true
#| code-summary: "Show the code"
movies <- data.frame(Title,Year,Duration,Rating,Votes)
print(head(movies, 15))
```

## Part III

### A) Top 5 and Bottom 5 Movies by Rating

#### Top 5 Movies by Rating

```{r}
#| code-fold: true
#| code-summary: "Show the code"

top_movies <- movies[order(movies$Rating, decreasing = TRUE),]

top5 <- head(top_movies, 5)
print(top5)
```

I've watched all of them multiple times, and I believe they deserve the ratings they received.

#### Bottom 5 Movies by Rating

```{r}
#| code-fold: true
#| code-summary: "Show the code"
# Arrange the data frame in descending order by Rating
bot_movies <- movies[order(movies$Rating, decreasing = TRUE),]

# Top 5 and bottom 5 movies based on user ratings
bottom5 <- tail(bot_movies, 5)
print(bottom5)
```

I haven't watched any of them, and I don't intend to. Just the IMDb rating can convey a lot about a movie. I am definitely biased against these films :)

### B) My Top 3 Favorite Turkish Movies

```{r}
#| code-fold: true
#| code-summary: "Show the code"
favorite_movies <-movies %>% filter(Title %in% c("Masumiyet", "Babam ve Oglum", "Yahsi Bati"))
print(favorite_movies)
```

I believe they deserve the ratings they received. The rating for Yahşi Batı could have been a bit higher. In my opinion, it's Cem Yılmaz's funniest movie, but some people think it's not as good as GORA and AROG.

### C)Plots

#### Average Ratings of Turkish Movies Over the Years

```{r}
#| code-fold: true
#| code-summary: "Show the code"
movies %>%
  group_by(Year) %>% summarize(ave_rating = mean(Rating)) %>%
  ggplot(aes(Year, ave_rating)) + geom_point() +
  labs(x = "Year", y = "Rating Averages") +
  ggtitle("Average Ratings of Turkish Movies Over the Years") +
  theme(plot.title = element_text(hjust = 0.5))
```

Over the years, it is observed that the rating of Turkish movies has decreased. I wonder about the reason behind this. I believe it might be due to the lack of meaningful stories and scripts.

#### Number of Movies Over the Years

```{r}
#| code-fold: true
#| code-summary: "Show the code"
ggplot(movies, aes(x = factor(Year))) +
  geom_bar(fill = "purple", color = "#FBDA21") +
  labs(x = "Year", y = "Number of Movies") +
  ggtitle("Number of Movies Over the Years") +
  theme_minimal() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90),
        plot.title = element_text(hjust = 0.5))
```

#### Average Ratings Over the Years

```{r}
#| code-fold: true
#| code-summary: "Show the code"
ggplot(movies, aes(x = Year, y = Rating, fill = factor(Year))) +
  geom_boxplot() +
  labs(x = "Year", y = "Rating") +
  ggtitle("Average Ratings Over the Years") +
  theme_minimal()+ theme(plot.title = element_text(hjust = 0.5))
```

### D)Votes and Ratings

#### Correlation between Votes and Ratings:

```{r}
#| code-fold: true
#| code-summary: "Show the code"
correlation <- cor(movies$Votes, movies$Rating)
print(correlation)
```

```{r}
#| code-fold: true
#| code-summary: "Show the code"
ggplot(movies, aes(x = Votes, y = Rating, color = factor(Rating))) +
  geom_point(color = "purple") +
  geom_smooth(method = "lm", se = FALSE, color = "#FBDA21", formula = y ~ x) +
  labs(x = "Votes", y = "Rating") +
  ggtitle("Scatter Plot of Votes vs Rating") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))
```

The value of 0.130875 represents a quite low correlation. In this case, we can say that there is a weak linear relationship between Votes and Ratings.

### E)Durations and Ratings

#### Correlation between Durations and Ratings:

```{r}
#| code-fold: true
#| code-summary: "Show the code"
correlation1 <- cor(movies$Duration, movies$Rating)
print(correlation1)
```

```{r}
#| code-fold: true
#| code-summary: "Show the code"
ggplot(movies, aes(x = Duration, y = Rating, color = factor(Rating))) +
  geom_point(color = "purple") +
  geom_smooth(method = "lm", se = FALSE, color = "#FBDA21", formula = y ~ x) +
  labs(x = "Duration", y = "Rating") +
  ggtitle("Scatter Plot of Votes vs Rating") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))
```

The value of 0.03356006 represents a quite low correlation. In this case, we can say that there is a weak linear relationship between Votes and Durations. When comparing Ratings with Votes and Rating with Durations, we can say that there is a stronger connection between Ratings and Votes.

## Part IV

### Turkish Movies Top 1000 Movies on IMDb

```{r}
#| code-fold: true
#| code-summary: "Show the code"
url3 <- "https://m.imdb.com/search/title/?title_type=feature&groups=top_1000&country_of_origin=TR"

title3 <- read_html(url3) %>% 
  html_elements(".ipc-title__text") %>% html_text()
title3 <- tail(head(title3,-1),-1)
title3 <- str_split(title3, " ", n=2)
title3 <- unlist(lapply(title3, function(x) {x[2]}))

year3 <- read_html(url3)%>%html_elements(".dli-title-metadata-item:nth-child(1)")
year3 <- html_text(year3)
year3 <- as.factor(year3)

top1000 <- data.frame(Title=title3,Year=year3)
print(top1000)
```

### Combining Data Frames

```{r}
#| code-fold: true
#| code-summary: "Show the code"
top1000$Year <- as.numeric(as.character(top1000$Year))

joineddata <- left_join(top1000,movies, by = c("Title", "Year"))
print(joineddata)
```

### Top 11 Turkish Movie Based on Rating

```{r}
#| code-fold: true
#| code-summary: "Show the code"
top_movies <- movies[order(movies$Rating, decreasing = TRUE),]

top11 <- head(top_movies, 11)
print(top11)
```

The first data frame does not have a single film that matches the IMDb top 1000. I believe the differences I observed when comparing the two tables are in the film years and votes. It seems that the Top 1000 includes more recent films with significantly higher votes. (Note: I don't know why CM101MMXI Fundamentals is in the second list 😊)
